Baseline centering problem

### 2018-11-23 paper/advup_uniquesol.tex
Adding relative V terminal value

\paragraph{Removing $b$?} Let us just fix $b=0$ in the above. The unique
solution for $V$ (with $\gamma<1$) is
\begin{equation}
V(s)=V^\pi(s)+\left(\frac{1-\gamma}{\alpha}-1\right)\E_{\tilde \rho} V^\pi
\end{equation}
and with $\alpha=1$ this is simply
\begin{equation}
V(s)=V^\pi(s)-\gamma \E_{\tilde \rho} V^\pi
\end{equation}

@@

>>>>

\paragraph{Removing $b$?} Let us just fix $b=0$ in the above. The unique
solution for $V$ (with $\gamma<1$) is
\begin{equation}
V(s)=V^\pi(s)+\left(\frac{1-\gamma}{\alpha}-1\right)\E_{\tilde \rho} V^\pi
\label{eq:relative-td}
\end{equation}
and with $\alpha=1$ this is simply
\begin{equation}
V(s)=V^\pi(s)-\gamma \E_{\tilde \rho} V^\pi
\end{equation}

@@

\paragraph{Relative $V$ terminal value in semi-episodic environments} When
faced with a semi-episodic environment, i.e. an environment where terminal
states exist, but some policies never reach them, the value of the relative
$V$ function corresponding to a policy $\pi$ that do not reach terminal states,
on a terminal state $t$ is given by
\begin{equation}
	V(t) = - \frac{\gamma}{1 - \gamma} \E_{\tilde{\rho}} V.
\end{equation}
The result is obtained from \eqref{eq:relative-td}, since $\E_{\tilde{\rho}} V = (1 - \gamma)
\E_{\tilde{\rho}} V^\pi$, and $V^\pi(t) = 0$.
